Exact Asymptotics for Causal Mediation Analysis

### 2024-06-25 notes/Consolidated Notes/Consolidated Notes.tex
Update consolidated notes
Send updated analysis to B & B

I'm just finishing-up my code for the binary response, binary mediator, mixed effects case. My analysis is running, but the output doesn't look right, so I need to do some debugging.

@@

@@

Standard reference for mediation analysis with binary outcome. Focuses on the causal inference aspects of the problem. Makes heavy use of the ``rare outcome'' assumption. Resulting model is sufficiently simple that UQ is easy.

@@

I don't have a whole lot to say here. I implemented the $\delta$-method based uncertainty quantification developed by B \& B for the total mediation effect. Please see the RMarkdown document and accompanying PDF called ``William Analysis.Rmd'' and ``William-Analysis.pdf'' for discussion and results.

@@

\bibliography{../Literature_Review/Lit_Review_Bib}

>>>>

I'm just finishing-up my code for the binary response, binary mediator, mixed effects case. My analysis is running, but the output doesn't look right so I need to do some debugging.

@@

\section{\citeauthor{Van10}}

In a sequence of papers over the early-to-mid 2010s, \citeauthor{Van10} developed much of the theory for causal-based mediation analysis. Unfortunately, they make extensive use of the ``rare event'' assumption. Nevertheless, many of their papers have been influential, and they are certainly worth cataloging here.

\subsection{\citet{Van09}}

This paper lays out the basic theoretical assumptions required for causal mediation analysis. These include consistency, composition and no unmeasured confounders. They also define the various direct and indirect effects which are typically of interest, and discuss how to estimate these effects using regression (provided, of course, that the necessary assumptions are satisfied). The focus is entirely on continuous outcome and mediator, although they do address conditional mediation effects given covariates/confounders, and averaging over the confounder(s) to recover marginal effects. Next, they give several pages' discussion of how to think about the various assumptions. Finally, an appendix gives proofs of the asserted regression-based formulas, alongside some simple uncertainty quantification.

This is really a foundational paper, and is worth citing in pretty much any work on causal mediation analysis.

This paper modifies the work of \citet{Van09} to handle a binary outcome, although the mediator is still taken to be continuous. Results are presented on odds-ratio scale. They set-up their analysis exactly, but then present their results under the rare-outcome assumption. As far as I can tell, this is done to simplify formulas. The estimators they end up with are sufficiently simple that uncertainty quantification is easy.

This paper is a standard reference for mediation analysis with a binary outcome.

\subsection{\citet{Val13}}

Extends the work of \citet{Van10} to include a binary mediator. Still uses the rare outcome assumption and only reports results on odds-ratio scale.

\subsection{\citet{Van13}}

This paper extends the work of \citet{Van09} to handle multiple mediators.

\subsection{\citet{Van14}}

This paper extends the work of \citet{Van09} by giving an alternative decomposition of the total effect. The goal of this decomposition is to separate mediation from interaction between the exposure and mediator.

\subsection{\citet{Van15}}

A book, which consolidates much of the work of this group from the previous decade.

@@

@@

I don't have a whole lot to say here. I implemented the $\delta$-method based uncertainty quantification developed by B \& B for the total mediation effect. Please see the PDF called ``William-Analysis.pdf'' for discussion and results.

@@

% \bibliography{../Literature_Review/Lit_Review_Bib}
\bibliography{../../Bib-Exact_Asymptotics}

### 2024-06-25 notes/William Analysis.Rmd
Send updated analysis to B & B

# Fewer large sample sizes
# all_Ns = c(100, 200, 500, 1000, 2000)
# all_Ns = c(200, 500, 1000, 2000)
# all_Ns = c(200, 500, 1000)
all_Ns = c(200, 500, 1000)

@@

# Random effects
sigma_a_0 = 0.2
sigma_a_1 = 0.2 * abs(a_1)
cor_a0_a1 = 0.2
cov_a0_a1 = sigma_a_0 * sigma_a_1 * cor_a0_a1
theta = c(sigma_a_0, sigma_a_1, cor_a0_a1)
Sigma_a = matrix(c(sigma_a_0^2, cov_a0_a1, cov_a0_a1, sigma_a_1^2), nrow = 2, ncol = 2)

sigma_b_0 = 0.2 * abs(b_0)
sigma_b_1 = 0.2 * abs(b_1)
cor_b0_b1 = 0.2
cov_b0_b1 = sigma_b_0 * sigma_b_1 * cor_b0_b1
gamma = c(sigma_b_0, sigma_b_1, cor_b0_b1)
Sigma_b = matrix(c(sigma_b_0^2, cov_b0_b1, cov_b0_b1, sigma_b_1^2), nrow = 2, ncol = 2)

# Number of clusters
all_Ks = c(5, 20, 50, 100)
# K=5

N_K_combs = expand.grid(N = all_Ns, K = all_Ks)

# Number of replicates for each sample size
# We use fewer here because model fitting takes longer
num_reps = 200

# Easier version of problem
all_Ns = c(200, 500)
all_Ks = c(5, 20)

sigma_a_0 = 0.5
sigma_a_1 = 0.5 * abs(a_1)
cor_a0_a1 = 0.5
cov_a0_a1 = sigma_a_0 * sigma_a_1 * cor_a0_a1
theta = c(sigma_a_0, sigma_a_1, cor_a0_a1)
Sigma_a = matrix(c(sigma_a_0^2, cov_a0_a1, cov_a0_a1, sigma_a_1^2), nrow = 2, ncol = 2)

sigma_b_0 = 0.5 * abs(b_0)
sigma_b_1 = 0.5 * abs(b_1)
cor_b0_b1 = 0.5
cov_b0_b1 = sigma_b_0 * sigma_b_1 * cor_b0_b1
gamma = c(sigma_b_0, sigma_b_1, cor_b0_b1)
Sigma_b = matrix(c(sigma_b_0^2, cov_b0_b1, cov_b0_b1, sigma_b_1^2), nrow = 2, ncol = 2)
```

@@

@@

tic()

set.seed(1)

# Containers for output
all_a_hats = list()
all_theta_hats = list()
all_b_hats = list()
all_gamma_hats = list()

all_M_covs = list()
all_Y_covs = list()

# Initialize cluster on my machine ----
# n_cores = 2
# n_cores = 10
n_cores = parallel::detectCores() - 1
my_cluster = makeCluster(n_cores, type = "PSOCK")
registerDoParallel(my_cluster)
clusterEvalQ(my_cluster,{
  library(MASS)
  library(lme4)
  library(merDeriv)
  source("../src/Helpers.R")
})
clusterExport(my_cluster, c("N_K_combs", "num_reps", "a_0", "a_1", "A_2", "a", "b_0", "b_1", "b_2", "B_3", "b", "Sigma_a", "theta", "Sigma_b", "gamma", "p_conf", "x_pred", "W_pred"))
clusterSetRNGStream(my_cluster, iseed = 1)

# output_bin_bin_ran = pblapply(seq_len(nrow(N_K_combs)), function(j){
# output_bin_bin_ran = pblapply(nrow(N_K_combs), function(j){
for(j in seq_len(nrow(N_K_combs))){
  n = N_K_combs[j, "N"]
  K = N_K_combs[j, "K"]

  clusterExport(my_cluster, c("n", "K"))

  print(paste0("j = ", j, " of ", nrow(N_K_combs),  " (n=", n, ", K=", K, ")"))

  # # Containers for output with this value of n
  # some_a_hats = list()
  # some_theta_hats = list()
  # some_b_hats = list()
  # some_gamma_hats = list()
  #
  # some_M_covs = list()
  # some_Y_covs = list()
  #
  # some_med_hats = list()
  # some_med_SEs = list()

  # for(i in 1:num_reps){
  some_output = pblapply(seq_len(num_reps), function(i){
    # print(paste0("n = ", n, ", K = ", K, ", i = ", i, " of ", num_reps))

    this_output = NULL

    # Use tryCatch to omit any datasets leading to convergence issues
    tryCatch({                                                                    ############## Un-quote
      all_Xs = list()
      all_Ws = list()

      # Consolidate groups
      X = do.call(c, all_Xs)
      W = do.call(rbind, all_Ws)
      M = do.call(c, all_Ms)
      Y = do.call(c, all_Ys)
      group = rep(1:K, each = n)

      ## M
      M_data = data.frame(M, X, W1 = W[, 1], W2 = W[, 2], W3 = W[,3], group = group)
      M_model = glmer(M ~ X + W1 + W2 + W3 + (1 + X | group), data = M_data, family = binomial(link = "logit"))
      M_model_info = attributes(VarCorr(M_model)$group)

      ### Fitted parameters
      a_hat = fixef(M_model)
      a_RE_sds = M_model_info$stddev
      a_RE_cor = M_model_info$correlation[2,1]
      theta_hat = c(a_RE_sds, a_RE_cor)
      if(any(is.nan(theta_hat))) stop("NaNs in theta_hat")  # Skip rest of current analysis if correlation is 0/0

      ### Estimated SE covariance matrix
      M_cov = vcov(M_model, full=TRUE, ranpar="sd")

      # some_a_hats[[i]] = a_hat
      # some_theta_hats[[i]] = theta_hat
      # some_M_covs[[i]] = M_cov

      ## Y
      Y_data = data.frame(Y, M, X, W1 = W[, 1], W2 = W[, 2], W3 = W[,3], group = group)
      Y_model = glmer(Y ~ M + X + W1 + W2 + W3 + (1 + X | group), data = Y_data, family = binomial(link = "logit"))
      Y_model_info = attributes(VarCorr(Y_model)$group)

      ### Fitted parameters
      b_hat = fixef(Y_model)
      b_RE_sds = Y_model_info$stddev
      b_RE_cor = Y_model_info$correlation[2,1]
      gamma_hat = c(b_RE_sds, b_RE_cor)
      if(any(is.nan(gamma_hat))) stop("NaNs in gamma_hat")  # Skip rest of current analysis if correlation is 0/0

      ### Estimated SE covariance matrix
      Y_cov = vcov(Y_model, full=TRUE, ranpar="sd")

      # some_b_hats[[i]] = b_hat
      # some_gamma_hats[[i]] = gamma_hat
      # some_Y_covs[[i]] = Y_cov

      ## Fixed-effects

      ## Linear predictors
      eta_hat = as.numeric(a_0_hat + a_x_hat*x_pred + W_pred%*%A_2_hat)
      zeta_hat = as.numeric(b_0_hat + b_x_hat * x_pred + W_pred %*% B_3_hat)

      ## Random effects covariances
      s_M_0 = a_RE_sds[1]
      s_M_x = a_RE_sds[2]
      rho_M = a_RE_cor

      ## Sigma functions
      sigma_M1 = sigma_fun(x_pred, s_M_0, s_M_x, rho_M)
      sigma_M2 = sigma_fun(x_pred + 1, s_M_x, s_M_0, rho_M)

      ## Mediation effect
      ### See Helpers.R for the function Phi, which computes the mediation effect on odds-ratio scale
      med_hat = Phi(eta_hat, zeta_hat, a_x_hat, b_m_hat, b_x_hat, sigma_M2, sigma_Y2, sigma_M1, sigma_Y1)
      # some_med_hats[[i]] = med_hat

      ## Gradient of OR wrt regression coefficients
      grad_Phi_obs = grad_Phi(eta_hat, zeta_hat, a_x_hat, b_m_hat, b_x_hat, sigma_M2, sigma_Y2, sigma_M1, sigma_Y1)
      grad_xi_obs = grad_xi(a_hat, theta_hat, b_hat, gamma_hat, x_pred, W_pred)
      d_Phi_d_GLMM_pars = grad_Phi_obs %*% grad_xi_obs

      ## Get asymptotic SE using delta method

      ### Build joint covariance matrix of regression coefficients
      M_length = nrow(M_cov)
      Y_length = nrow(Y_cov)
      joint_cov = matrix(0, nrow = M_length + Y_length, ncol = M_length +
      Y_length)
      joint_cov[1:M_length, 1:M_length] = M_cov
      joint_cov[(M_length + 1):(M_length + Y_length), (M_length + 1):(M_length +
      Y_length)] = Y_cov

      ### Convert to asymptotic covariance matrix
      asymp_reg_cov = n * joint_cov

      ### Pre- and post-multiply asymptotic covariance by gradient of Phi wrt GLMM parameters
      med_asymp_var = d_Phi_d_GLMM_pars %*% asymp_reg_cov %*% t(d_Phi_d_GLMM_pars)

      ### Get small-sample standard error
      med_asymp_SE = sqrt(med_asymp_var)
      med_SE = med_asymp_SE / sqrt(n)

      # some_med_SEs[[i]] = med_SE

      this_output = list(a_hat = a_hat, theta_hat = theta_hat, b_hat = b_hat, gamma_hat = gamma_hat, M_cov = M_cov, Y_cov = Y_cov, med_hat = med_hat, med_SE = med_SE)
    # }, error = function(e){grad_Phi_obs <<- e}) # For troubleshooting parallel errors
    }, error = function(e){})                                                       ############ Un-quote

    return(this_output)

  }, cl = my_cluster)
  # })

  # Store output for current values of n and K

  all_a_hats[[j]] = lapply(some_output, function(x) x$a_hat)
  all_theta_hats[[j]] = lapply(some_output, function(x) x$theta_hat)
  all_b_hats[[j]] = lapply(some_output, function(x) x$b_hat)
  all_gamma_hats[[j]] = lapply(some_output, function(x) x$gamma_hat)
  all_M_covs[[j]] = lapply(some_output, function(x) x$M_cov)
  all_Y_covs[[j]] = lapply(some_output, function(x) x$Y_cov)
  all_med_hats[[j]] = lapply(some_output, function(x) x$med_hat)
  all_med_SEs[[j]] = lapply(some_output, function(x) x$med_SE)
}

runtime = toc()

parallel::stopCluster(my_cluster)

# Save output
# save(N_K_combs, all_a_hats, all_theta_hats, all_b_hats, all_gamma_hats, all_M_covs, all_Y_covs, all_med_hats, all_med_SEs, runtime, file = "William-Analysis_cache/MC-bin-bin-mix.RData")
# load("D:/OneDrive/OneDrive - Simon Fraser University (1sfu)/Research/Postdoc/Exact_Asymptotics/notes/William-Analysis_cache/MC-bin-bin-mix.RData", verbose = TRUE)
```

@@

<!-- I'm now trying to figure out what's causing an error which only occurs on knit. Trying to isolate it in the following code chunk: -->

<!-- ```{r} -->
<!-- load("D:/OneDrive/OneDrive - Simon Fraser University (1sfu)/Research/Postdoc/Exact_Asymptotics/notes/William-Analysis_cache/MC-bin-bin-mix.RData", verbose = TRUE) -->

<!-- # print(all_med_hats) -->
<!-- ``` -->

@@

<!-- I don't really understand the results I'm getting here. It should help if I can compare my estimates of the mediation effect with the true value. -->

<!-- ```{r} -->
<!-- load("../data/Exact_Asymptotics/Bin-Bin-Mix_Results.RData") -->

<!-- true_med = Phi_of_xi(a, theta, b, gamma, x_pred, W_pred) -->

<!-- load("William-Analysis_cache/latex/unnamed-chunk-37_44bd8d1152289e689fbff9185d17042c.RData", ex <- new.env()) -->
<!-- ``` -->

>>>>

### Easier version of problem ###

all_Ns = c(50, 200, 500, 1000)  # Sample size for each cluster
all_Ks = c(5, 20, 50)           # Number of clusters
N_K_combs = expand.grid(N = all_Ns, K = all_Ks)

# Number of replicates for each sample size
num_reps = 200

@@

# Random effects
sigma_a_0 = 0.5
sigma_a_1 = 0.5 * abs(a_1)
cor_a0_a1 = 0.5
cov_a0_a1 = sigma_a_0 * sigma_a_1 * cor_a0_a1
theta = c(sigma_a_0, sigma_a_1, cor_a0_a1)
Sigma_a = matrix(c(sigma_a_0^2, cov_a0_a1, cov_a0_a1, sigma_a_1^2), nrow = 2, ncol = 2)

sigma_b_0 = 0.5 * abs(b_0)
sigma_b_1 = 0.5 * abs(b_1)
cor_b0_b1 = 0.5
cov_b0_b1 = sigma_b_0 * sigma_b_1 * cor_b0_b1
gamma = c(sigma_b_0, sigma_b_1, cor_b0_b1)
Sigma_b = matrix(c(sigma_b_0^2, cov_b0_b1, cov_b0_b1, sigma_b_1^2), nrow = 2, ncol = 2)

### Harder version ###

# # Fewer large sample sizes
# # all_Ns = c(100, 200, 500, 1000, 2000)
# # all_Ns = c(200, 500, 1000, 2000)
# # all_Ns = c(200, 500, 1000)
# # all_Ns = c(200, 500, 1000)
# 
# Values of X and W for which we compute the total effect
# x_pred = 0
# W_pred = c(1,1,1)
# 
# # Fixed effects for intercepts
# a_0 = 0
# a = c(a_0, a_1, A_2)
# b_0 = -0.5
# b = c(b_0, b_1, b_2, B_3)
# 
# # # Random effects
# # sigma_a_0 = 0.2
# # sigma_a_1 = 0.2 * abs(a_1)
# # cor_a0_a1 = 0.2
# # cov_a0_a1 = sigma_a_0 * sigma_a_1 * cor_a0_a1
# # theta = c(sigma_a_0, sigma_a_1, cor_a0_a1)
# # Sigma_a = matrix(c(sigma_a_0^2, cov_a0_a1, cov_a0_a1, sigma_a_1^2), nrow = 2, ncol = 2)
# # 
# # sigma_b_0 = 0.2 * abs(b_0)
# # sigma_b_1 = 0.2 * abs(b_1)
# # cor_b0_b1 = 0.2
# # cov_b0_b1 = sigma_b_0 * sigma_b_1 * cor_b0_b1
# # gamma = c(sigma_b_0, sigma_b_1, cor_b0_b1)
# # Sigma_b = matrix(c(sigma_b_0^2, cov_b0_b1, cov_b0_b1, sigma_b_1^2), nrow = 2, ncol = 2)
# 
# # Number of clusters
# # all_Ks = c(5, 20, 50, 100)
# # K=5
# 
# # N_K_combs = expand.grid(N = all_Ns, K = all_Ks)
# 
# # Number of replicates for each sample size
# # We use fewer here because model fitting takes longer
# num_reps = 200

@@

# Commented out to avoid lengthy runtime

@@

# tic()
# 
# set.seed(1)
# 
# # Containers for output
# all_a_hats = list()
# all_theta_hats = list()
# all_b_hats = list()
# all_gamma_hats = list()
# 
# all_M_covs = list()
# all_Y_covs = list()
# 
# all_med_hats = list()
# all_med_SEs = list()
# 
# 
# # Initialize cluster on my machine ----
# # n_cores = 2
# n_cores = 10
# # n_cores = parallel::detectCores() - 1
# my_cluster = makeCluster(n_cores, type = "PSOCK")
# registerDoParallel(my_cluster)
# clusterEvalQ(my_cluster,{
#   library(MASS)
#   library(lme4)
#   library(merDeriv)
#   source("../src/Helpers.R")
# })
# clusterExport(my_cluster, c("N_K_combs", "num_reps", "a_0", "a_1", "A_2", "a", "b_0", "b_1", "b_2", "B_3", "b", "Sigma_a", "theta", "Sigma_b", "gamma", "p_conf", "x_pred", "W_pred"))
# clusterSetRNGStream(my_cluster, iseed = 1)
# 
# # output_bin_bin_ran = pblapply(seq_len(nrow(N_K_combs)), function(j){
# # output_bin_bin_ran = pblapply(nrow(N_K_combs), function(j){
# for(j in seq_len(nrow(N_K_combs))){
#   n = N_K_combs[j, "N"]
#   K = N_K_combs[j, "K"]
# 
#   clusterExport(my_cluster, c("n", "K"))
# 
#   print(paste0("j = ", j, " of ", nrow(N_K_combs),  " (n=", n, ", K=", K, ")"))
# 
# 
#   # # Containers for output with this value of n
#   # some_a_hats = list()
#   # some_theta_hats = list()
#   # some_b_hats = list()
#   # some_gamma_hats = list()
#   #
#   # some_M_covs = list()
#   # some_Y_covs = list()
#   #
#   # some_med_hats = list()
#   # some_med_SEs = list()
# 
#   # for(i in 1:num_reps){
#   some_output = pblapply(seq_len(num_reps), function(i){
#     # print(paste0("n = ", n, ", K = ", K, ", i = ", i, " of ", num_reps))
# 
#     this_output = NULL
# 
#     # Use tryCatch to omit any datasets leading to convergence issues
#     tryCatch({                                                                    ############## Un-quote
#       all_Xs = list()
#       all_Ws = list()
# 
#       for(k in 1:K){
#         X = rnorm(n, mean=0, sd=1)
#         W = matrix(rnorm(n*p_conf, mean=0, sd=1), nrow = n, ncol = p_conf)
# 
#         all_Xs[[k]] = X
#         all_Ws[[k]] = W
#       }
# 
#       # Generate M
#       all_Ms = list()
#       for(k in 1:K){
#         eta_vec_fixed = a_0 + a_1*all_Xs[[k]] + all_Ws[[k]]%*%A_2
# 
#         ## Add random effects
#         a_ran = mvrnorm(1, mu = rep(0, 2), Sigma = Sigma_a)
#         eta_vec = eta_vec_fixed + a_ran[1] + a_ran[2]*all_Xs[[k]]
# 
#         ## Generate M
#         p_M_vec = expit(eta_vec)
#         M = rbinom(n, size = 1, prob = p_M_vec)
#         all_Ms[[k]] = M
#       }
# 
#       # Generate Y
#       all_Ys = list()
#       for(k in 1:K){
#         zeta_vec_fixed = b_0 + b_1*all_Ms[[k]] + b_2 * all_Xs[[k]] + all_Ws[[k]]%*%B_3
# 
#         ## Add random effects
#         b_ran = mvrnorm(1, mu = rep(0, 2), Sigma = Sigma_b)
#         zeta_vec = zeta_vec_fixed + b_ran[1] + b_ran[2]*all_Xs[[k]]
# 
#         ## Generate Y
#         p_Y_vec = expit(zeta_vec)
#         Y = rbinom(n, size = 1, prob = p_Y_vec)
#         all_Ys[[k]] = Y
#       }
# 
# 
#       # Consolidate groups
#       X = do.call(c, all_Xs)
#       W = do.call(rbind, all_Ws)
#       M = do.call(c, all_Ms)
#       Y = do.call(c, all_Ys)
#       group = rep(1:K, each = n)
# 
# 
#       # Fit models
# 
#       ## M
#       M_data = data.frame(M, X, W1 = W[, 1], W2 = W[, 2], W3 = W[,3], group = group)
#       M_model = glmer(M ~ X + W1 + W2 + W3 + (1 + X | group), data = M_data, family = binomial(link = "logit"))
#       M_model_info = attributes(VarCorr(M_model)$group)
# 
#       ### Fitted parameters
#       a_hat = fixef(M_model)
#       a_RE_sds = M_model_info$stddev
#       a_RE_cor = M_model_info$correlation[2,1]
#       theta_hat = c(a_RE_sds, a_RE_cor)
#       if(any(is.nan(theta_hat))) stop("NaNs in theta_hat")  # Skip rest of current analysis if correlation is 0/0
# 
#       ### Estimated SE covariance matrix
#       M_cov = vcov(M_model, full=TRUE, ranpar="sd")
# 
#       # some_a_hats[[i]] = a_hat
#       # some_theta_hats[[i]] = theta_hat
#       # some_M_covs[[i]] = M_cov
# 
# 
#       ## Y
#       Y_data = data.frame(Y, M, X, W1 = W[, 1], W2 = W[, 2], W3 = W[,3], group = group)
#       Y_model = glmer(Y ~ M + X + W1 + W2 + W3 + (1 + X | group), data = Y_data, family = binomial(link = "logit"))
#       Y_model_info = attributes(VarCorr(Y_model)$group)
# 
#       ### Fitted parameters
#       b_hat = fixef(Y_model)
#       b_RE_sds = Y_model_info$stddev
#       b_RE_cor = Y_model_info$correlation[2,1]
#       gamma_hat = c(b_RE_sds, b_RE_cor)
#       if(any(is.nan(gamma_hat))) stop("NaNs in gamma_hat")  # Skip rest of current analysis if correlation is 0/0
# 
#       ### Estimated SE covariance matrix
#       Y_cov = vcov(Y_model, full=TRUE, ranpar="sd")
# 
#       # some_b_hats[[i]] = b_hat
#       # some_gamma_hats[[i]] = gamma_hat
#       # some_Y_covs[[i]] = Y_cov
# 
# 
# 
#       # Estimate mediation effect
# 
#       ## Fixed-effects
# 
#       a_0_hat = a_hat[1]
#       a_x_hat = a_hat[2]
#       A_2_hat = a_hat[3:5]
# 
#       b_0_hat = b_hat[1]
#       b_m_hat = b_hat[2]
#       b_x_hat = b_hat[3]
#       B_3_hat = b_hat[4:6]
# 
# 
#       ## Linear predictors
#       eta_hat = as.numeric(a_0_hat + a_x_hat*x_pred + W_pred%*%A_2_hat)
#       zeta_hat = as.numeric(b_0_hat + b_x_hat * x_pred + W_pred %*% B_3_hat)
# 
# 
#       ## Random effects covariances
#       s_M_0 = a_RE_sds[1]
#       s_M_x = a_RE_sds[2]
#       rho_M = a_RE_cor
# 
#       s_Y_0 = b_RE_sds[1]
#       s_Y_x = b_RE_sds[2]
#       rho_Y = b_RE_cor
# 
# 
#       ## Sigma functions
#       sigma_M1 = sigma_fun(x_pred, s_M_0, s_M_x, rho_M)
#       sigma_M2 = sigma_fun(x_pred + 1, s_M_x, s_M_0, rho_M)
# 
#       sigma_Y1 = sigma_fun(x_pred, s_Y_0, s_Y_x, rho_Y)
#       sigma_Y2 = sigma_fun(x_pred + 1, s_Y_x, s_Y_0, rho_Y)
# 
#       ## Mediation effect
#       ### See Helpers.R for the function Phi, which computes the mediation effect on odds-ratio scale
#       med_hat = Phi(eta_hat, zeta_hat, a_x_hat, b_m_hat, b_x_hat, sigma_M2, sigma_Y2, sigma_M1, sigma_Y1)
#       # some_med_hats[[i]] = med_hat
# 
# 
# 
# 
# 
#       # Estimate SE
# 
#       ## Gradient of OR wrt regression coefficients
#       grad_Phi_obs = grad_Phi(eta_hat, zeta_hat, a_x_hat, b_m_hat, b_x_hat, sigma_M2, sigma_Y2, sigma_M1, sigma_Y1)
#       grad_xi_obs = grad_xi(a_hat, theta_hat, b_hat, gamma_hat, x_pred, W_pred)
#       d_Phi_d_GLMM_pars = grad_Phi_obs %*% grad_xi_obs
# 
#       ## Get asymptotic SE using delta method
# 
#       ### Build joint covariance matrix of regression coefficients
#       M_length = nrow(M_cov)
#       Y_length = nrow(Y_cov)
#       joint_cov = matrix(0, nrow = M_length + Y_length, ncol = M_length +
#       Y_length)
#       joint_cov[1:M_length, 1:M_length] = M_cov
#       joint_cov[(M_length + 1):(M_length + Y_length), (M_length + 1):(M_length +
#       Y_length)] = Y_cov
# 
#       ### Convert to asymptotic covariance matrix
#       asymp_reg_cov = n * joint_cov
# 
#       ### Pre- and post-multiply asymptotic covariance by gradient of Phi wrt GLMM parameters
#       med_asymp_var = d_Phi_d_GLMM_pars %*% asymp_reg_cov %*% t(d_Phi_d_GLMM_pars)
# 
#       ### Get small-sample standard error
#       med_asymp_SE = sqrt(med_asymp_var)
#       med_SE = med_asymp_SE / sqrt(n)
# 
#       # some_med_SEs[[i]] = med_SE
# 
#       this_output = list(a_hat = a_hat, theta_hat = theta_hat, b_hat = b_hat, gamma_hat = gamma_hat, M_cov = M_cov, Y_cov = Y_cov, med_hat = med_hat, med_SE = med_SE)
#     # }, error = function(e){grad_Phi_obs <<- e}) # For troubleshooting parallel errors
#     }, error = function(e){})                                                       ############ Un-quote
# 
#     return(this_output)
# 
# 
#   }, cl = my_cluster)
#   # })
# 
#   # Store output for current values of n and K
# 
#   all_a_hats[[j]] = lapply(some_output, function(x) x$a_hat)
#   all_theta_hats[[j]] = lapply(some_output, function(x) x$theta_hat)
#   all_b_hats[[j]] = lapply(some_output, function(x) x$b_hat)
#   all_gamma_hats[[j]] = lapply(some_output, function(x) x$gamma_hat)
#   all_M_covs[[j]] = lapply(some_output, function(x) x$M_cov)
#   all_Y_covs[[j]] = lapply(some_output, function(x) x$Y_cov)
#   all_med_hats[[j]] = lapply(some_output, function(x) x$med_hat)
#   all_med_SEs[[j]] = lapply(some_output, function(x) x$med_SE)
# }
# 
# 
# runtime = toc()
# 
# parallel::stopCluster(my_cluster)

# Save output
# save(N_K_combs, all_a_hats, all_theta_hats, all_b_hats, all_gamma_hats, all_M_covs, all_Y_covs, all_med_hats, all_med_SEs, runtime, file = "William-Analysis_cache/MC-bin-bin-mix.RData")
load("William-Analysis_cache/MC-bin-bin-mix.RData", verbose = TRUE)
```

@@

@@
